%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[12pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]

\newcommand{\comment}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}
\usepackage{inputenc}
\usepackage{ifthen}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     VARIABLE SET TO MAKE RESUME ATS COMPATIBLE
%     SET ATS as 1 for the resume to be ATS friendly
%     SET ATS as 0 otherwise
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcounter{ats}
\setcounter{ats}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Mukesh} {Arambakam}
\address{Apartment 20, St. James's Court, Echlin Street, Dublin 8}
%%% Social
\ifthenelse{\value{ats}=1}
{
\infomobile{(+353) 89-4960-450}
\infoemail{amukesh.mk@gmail.com}
\infohome{http://mukeshmk.github.io/}
\infolinkedin{https://www.linkedin.com/in/mukeshmk95/}
}
{
\mobile{(+353) 89-4960-450}
\email{amukesh.mk@gmail.com}
\homepage{\href{http://mukeshmk.github.io/}{mukeshmk.github.io}}
\github{mukeshmk}
\linkedin{mukeshmk95}
\stackoverflow{4014678}{mukesh-a}
}

\position{
    {\enskip\cdotp\enskip}
    Data Scientist in the Making
    {\enskip\cdotp\enskip}
    }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {}
  {Mukesh Arambakam}
  {\thepage}

\begin{document}
%%% Make a header for CV with personal data
\makecvheader

%% Summary
\cvsection{Personal Summary}
\vspace{-1.5ex}
\begin{cventries}
\lettertextstyle{
    \begin{flushleft}
    \quad\quad\quad I am a Bi-Lingual (English and Tamil), B.Tech Graduate and a Master’s student from Trinity College of Dublin, with 2 years of work experience at Oracle India, Pvt. Ltd. I am highly skilled with computers and have an excellent communication and inter-personal skills, with a background in retail and cash-handling. I am flexible to work at any time and all days of the week.
    \end{flushleft}
  }
\end{cventries}

%% Skills
\cvsection{Skills}
\begin{cvskills}
    \cvskill
        {Soft Skills:}
        {Communication, Problem Solving, Critical Thinking, Team Player, Time Management, Leadership, Negotiation}
    \cvskill
        {Computer Skills:}
        {MS Office (Excel), Scheduling and other Advanced Computer Skills}
\end{cvskills}

%% Experience
\cvsection{Relevant Experience}
\begin{cventries}
\cventry
    {Retail Store Employee}
    {Latta Super Market}
    {Chennai, India}
    {Jan. 2018 - Apr, 2018}
    {
      \begin{cvitems}
        \item {Customer Assistant and Cashier.}
        \item {Handled customer relations and inquires.}
        \item {Increased sales through engagement with customers, though suggestive selling and sharing product knowledge.}
        \item {Kept clientele informed by notifying them of preferred customer sales and other merchandise of potential interest.}
      \end{cvitems}
    }
\cventry
    {Shop Assistant}
    {Amrita Super Market}
    {Coimbatore, India}
    {Jun. 2016 - May, 2017}
    {
      \begin{cvitems}
        \item {Customer Assistant and Cashier.}
        \item {Managed financial transactions.}
        \item {Assisted with inventory, including receiving and stocking merchandise.}
      \end{cvitems}
    }
\end{cventries}

\vspace{-2.0ex}
%% Other Experience
\cvsection{Other Experience}
\begin{cventries}
\cventry
    {Data Scientist Intern}
    {Augray Private, Ltd.}
    {Remote Work}
    {Jun. 2020 - Aug, 2020}
    {}
\cventry
    {Application Engineer}
    {Oracle India, Pvt. Ltd.}
    {Bangalore, India}
{Jul. 2017 - Aug. 2019}
    {}
\end{cventries}

\vspace{-2.0ex}
%% Education
\cvsection{Education}
\begin{cventries}
  \cventry
    {M.Sc. in Data Science}
    {Trinity College of Dublin}
    {expecting for 1:1}
    {2019 - 2020}
    {}
  \cventry
    {B.Tech. in Computer Science and Engineering}
    {Amrita School of Engineering}
    {CGPA: 8.37/10.0}
    {2013 - 2017}
    {}
\end{cventries}

\end{document}