\cvsection{Work Experience}
\begin{cventries}
  \cvexperience
    {Senior Machine Learning Engineer (IC-3)}
    {Oracle Corporation}
    {}
    {}
    {Nov. 2020 - Current}
    {
      \begin{cvitemswithheading}
        {Language Detection Enhancements:}
        \item {Expanded language detection coverage from 45 to 192 languages.}
        \item {Introduced a 3-stage hierarchical language detection architecture to differentiate sub-cultural languages.}
        \item {Improved language detection accuracy by 90\% for very short strings (<12 characters).}
        \item {Refactored the codebase using robust system design patterns and FastAPI to significantly boost performance by 3x times.}
        \item {Packaged and published ONNX models with architecture-aware configurations for cross-compatibility.}
        \item {Used architecture-specific optimizations and model quantization to reduce memory footprint by 50\%.}
      \end{cvitemswithheading}
    }
  \cvexpproj
  {
    \begin{cvitemswithheading}
        {LLMs \& Agentic AI Systems:}
        \item {Launched an agentic AI system with LangGraph, supporting 10k+ LLM calls to Translation \& LangDetect MCP servers.}
        \item {Implemented 2 RAG systems with vector databases for domain-specific data extraction and translation enhancement.}
        \item {Engineered 5+ prompt engineering solutions for back-translation, domain classification, post-editing, and data generation with sophisticated tool calling mechanisms.}
        \item {Used prompt chaining techniques for multi-step LLM workflows including translation evaluation, iterative improvement, pivot-translation and post-editing.}
      \end{cvitemswithheading}
  }
  \cvexpproj
  {
    \begin{cvitemswithheading}
        {Data Processing \& Analysis}
         \item {Developed a dataset analysis framework from scratch for MT training data statistics, working across 40+ language pairs.}
        \item {Built a monolingual data generator for low-resource languages increasing synthetic data coverage by 30–40\%.}
        \item {Designed a cross-lingual vocabulary gap detection tool leveraging n-gram and embeddings, improving coverage by 20\%.}
        \item {Enhanced data-cleaning by reducing noise by 10\% using alignment models, length ratios, and toxicity checks.}
        \item {Used zero-shot and few-shot learning for domain classification and data categorization tasks.}
    \end{cvitemswithheading}
  }
  \cvexpproj
  {
    \begin{cvitemswithheading}
        {Engine Training, Fine-Tuning \& Optimization:}
        \item {Updated the Training pipeline to generate word alignment, length ratio models for data cleaning and evaluations.}
        \item {Developed a Monolingual Engine Training pipeline and de-prioritized the tagged monolingual data during training.}
        \item {Fine-tuned translation models using PEFT techniques for efficient adaptation to domain-specific tasks.}
        \item {Applied quantization strategies (QLoRA) for LLM deployment, cutting resource usage by 40\% in production.}
      \end{cvitemswithheading}
  }
  \cvexpproj
  {
    \begin{cvitemswithheading}
        {Advanced Evaluation \& Quality Assurance}
        \item {Re-engineered translation evaluation repository with modern architectures, boosting performance by 25\%.}
        \item {Designed custom translation quality rubrics with linguists and applied LLM-as-a-Judge via direct assessment.}
        \item {Integrated G-Eval metric and "LLM as a Judge" framework for comprehensive LLM-based translation assessment.}
        \item {Created visualization for evaluation scores using custom-built tools.}
        \item {Expanded evaluation framework with 5 new metrics: Comet, XComet, BERTScore, CometQE, and length-ratio checks.}
        \item {Assessed LLM translation consistency with Translate-then-Evaluate and LLM-as-a-Judge, raising accuracy by 20\%.}
    \end{cvitemswithheading}
  }
  \cvexperiencecontinued
    {Applications Engineer (IC-2)}
    {}
    {June 2019 - Aug. 2019}
    {
      \begin{cvitems}
        \item {Coordinated with multiple global teams, business analysts, and stakeholders to develop a cross-platform application.}
        \item {Lead developer in overhauling the project security flow of the Product and introduced 2 new features.}
        \item {Implemented a micro-service which communicates between tenants in a \textit{Multi-Tenant Architecture}.}
        \item {Mentored 10 junior team members, and provided insights about the product's internal working and underlying tools.}
      \end{cvitems}
    }
  \cvexperiencecontinued
    {Applications Developer (IC-1)}
    {}
    {July 2017 - May 2019}
    {
      \begin{cvitems}
        \item {\textbf{Certificate of Appreciation:} For \textit{outstanding contribution} to the Product's Development.}
        \item {Assumed a pivotal role in the development of 3 core features of the product along with my team members.}
        \item {Optimized the performance of an internal module's filter framework with the use of dynamic SQL queries by 30\%.}
        \item {Improved the performance of \textit{search framework} by 20\%, using query optimization techniques.}
      \end{cvitems}
    }


\end{cventries}
