\cvsection{Work Experience}
\begin{cventries}
  \cvexperience
    {Senior Machine Learning Engineer (IC-3)}
    {Oracle Corporation}
    {}
    {
    \begin{cvitems}
    \hspace{-2ex}
        Oracle is a world leader in database management software, cloud-engineered systems, and enterprise software products. I worked as part of the Internal Product Solutions Domain, with the Neural Machine Translation (NMT) Team
    \end{cvitems}
    \vspace{-2ex}
    }
    {Nov. 2020 - Current}
    {
      \begin{cvitems}
        \item {Lead Researcher and Developer for creating Domain specific Machine Translation models.}
        \item {Fine-tuned various state-of-the-art pre-trained LLMs using the Transformers library, including BERT, RoBERTa, etc.}
        \item {Developed and implemented novel data cleaning techniques to improve the quality of training data.}
        \item {Involved in the Research and Development of techniques used in Dataset Analysis, Data Cleaning, and Engine Evaluation}
        \item {Added new metrics to the existing engine evaluation pipeline, including TER, COMET, and METEOR, to improve the accuracy and comprehensiveness of the evaluation.}
        \item {Responsible for various stages of development in the NMT Pipeline: Data Cleaning, Model Training, and Evaluation}
        \item {Developed a tool to create and use Monolingual data for model fine-tuning.}
        \item {Created a tool to generate synthetic data for NMT that was used to improve the accuracy of the model by 15\%.}
        \item {Worked with a team of linguists to develop new MT datasets for various domains. These datasets were then used to train new NMT models that achieved a 15\% improvement in accuracy over the previous state-of-the-art models.}
      \end{cvitems}
    }
  \cvexperiencecontinued
    {Applications Engineer (IC-2)}
    {}
    {June 2019 - Aug. 2019}
    {
      \begin{cvitems}
        \item {Coordinated with multiple global teams, business analysts, and stakeholders to develop a cross-platform application.}
        \item {Lead developer in overhauling the project security flow of the Product and introduced 2 new features.}
        \item {Implemented a micro-service which communicates between tenants in a \textit{Multi-Tenant Architecture}.}
        \item {Mentored 10 junior team members, and provided insights about the product's internal working and underlying tools.}
      \end{cvitems}
    }
  \cvexperiencecontinued
    {Applications Developer (IC-1)}
    {}
    {July 2017 - May 2019}
    {
      \begin{cvitems}
        \item {\textbf{Certificate of Appreciation:} For \textit{outstanding contribution} to the Product's Development.}
        \item {Assumed a pivotal role in the development of 3 core features of the product along with my team members.}
        \item {Optimized the performance of an internal module's filter framework with the use of dynamic SQL queries by 30\%.}
        \item {Improved the performance of \textit{search framework} by 20\%, using query optimization techniques.}
      \end{cvitems}
    }
\comment{
  \cvexperience
    {Data Science Intern}
    {Augray Private, Ltd.}
    {}
    {
    \begin{cvitems}
    \hspace{-2ex}
        Augray helps businesses thrive in Sales, Marketing, and operational improvements using eXtended Reality. I worked on a PoC of a new product for the company using Python, TensorFlow, Keras, Pandas, OpenCV, and other technologies to build a CNN model.
    \end{cvitems}
    \vspace{-2ex}
    }
    {July 2020 - Sept. 2020}
    {
      \begin{cvitems}
        \item {Part of a global team of 6, where we materialized an Augmented Reality based application.}
        \comment {Refined the image and video preprocessing procedure for the application.}
        \comment {Built supervised models to identify \& extract features from images using concepts like backpropagation \& ReLU}
        \item {Used data extraction, exploration, and transformation techniques to discover opportunities \& identify trends.}
        \comment {Used techniques like manipulating, transforming, and analyzing complex data at a large scale}
        \item {Part of the Research and Development team instrumental in shaping the Convolutional Neural Network.}
      \end{cvitems}
    }
    }
  \comment{
  \cvexperiencecontinued
    {Graduate Intern}
    {}
    {Jan. 2017 - June 2017}
    {
      \begin{cvitems}
        \item {Worked as a Selenium Automation Engineer, automating over 100 test cases.}
        \item {Maintained high product quality standards while working as a Quality Assurance Engineer.}
      \end{cvitems}
    }
    }
\comment{
  \cventry
    {Intern}
    {Cisco Systems Private, Ltd.}
    {}
    {Oct. 2016 - Mar. 2017}
    {
      \begin{cvitems}
        \item {Involved in the platform transformation process of an internal product: \textbf{Cordys Process System}.}
        \item {Part of a team of 5, who designed the UX, Architecture, and Database Schema for the application.}
      \end{cvitems} 
    }
  \cventry
    {Intern}
    {Hitachi Solutions, Ltd.}
    {}
    {July 2016 - July 2016}
    {
      \begin{cvitems}
        \item {Created a web application with an authentication system.}    
      \end{cvitems}
    }
}
\end{cventries}
